---
title: "How to use processMetaDataMatrix"
author: "Jia Yan Ng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{processMetaDataMatrix}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>"
)
```

```{r setup}
library(scicloud)
```
### Prerequisite
Finish running `metaMatrix` function and provide its output as one of the inputs to this function

### When to use processMetaDataMatrix
`processMetaDataMatrix` function is the first function called within the wrapper function `ordinationCluster`. If you would like to run the analysis step by step. This should be the first function to be called after running `createTextMatrixFromPDF` function. This function takes output of `createTextMatrixFromPDF` function and process the matrix by removing all irrelevant information such as email address, URLs, references, punctuation, math equations found in each of the PDF. The options for the language and stem words can be defined through _control_ argument in the function. The inputs to this _control_ argument are mandatory and must be of _list()_ object containing the following: 

language
  : expect a valid string object which defines the stopwords to be filtered. (e.g. "english" or "SMART") 

stemWords
  : expect a boolean object which defines whether stem words should be removed from the texts.

saveToWd
  : expect a boolean object which defines whether the output of the function should be save as a RDS object in the working directory. 

ordinationFunction
  : expect a boolean object which determines whether a long message should be printed in the console. 

Users are also provided with the options to ignore certain words or to keep certain words in the analysis. This can be defined through _ignoreWords_ and _keepWordsFile_ arguments respectively. By default these two arguments are set to be empty and they are optional.  

ignoreWords
  : reserve the list of words as a vector of words to be ignored in the analysis

keepWordsFile
  : the file path to a CSV that specifies which words to keep in the analysis. If provided, the analysis will only keep these words and all other words will be disregarded.

---
**Example of use:**
```
metaMatrix <- createTextMatrixFromPDF(saveToWd = FALSE)

processedMatrix <- processMetaDataMatrix(metaMatrix, list(language = "SMART", stemWords = TRUE, stemWords, saveToWd = FALSE, ordinationFunction = FALSE), ignoreWords = c("Abstract", "Bulletin", "Editor"))
```


